\chapter{Introduction}

In diesen Dateien finden Sie die Beispiele aus den youtube-Videos:

\url{https://www.youtube.com/playlist?list=PLwlC-XZXtzhg4fQiZQAsXIMSRW-iZtnTQ}

Zusätzlich haben wir noch infos von \cite{goklerPredictionDemandRed2022} erhalten.
Ebenso kann man textcite verwenden: \textcite{goklerPredictionDemandRed2022} oder auch \textcite{pereiraPerformanceTimeseriesMethods2004}


\section{Background}

\section{Time series and forecasting}

--> über forecasting schreiben:

"Some things are easier to forecast than others. The time of the sunrise tomorrow morning can be forecast precisely. 
On the other hand, tomorrow’s lotto numbers cannot be forecast with any accuracy. The predictability of an event or a 
quantity depends on several factors including:
    how well we understand the factors that contribute to it;
    how much data is available;
    how similar the future is to the past;
    whether the forecasts can affect the thing we are trying to forecast.
" 
https://otexts.com/fpp3/what-can-be-forecast.html, 02.06.2025

"Often in forecasting, a key step is knowing when something can be forecast accurately, 
and when forecasts will be no better than tossing a coin. Good forecasts capture the genuine 
patterns and relationships which exist in the historical data, but do not replicate past events that will not occur again.
"
https://otexts.com/fpp3/what-can-be-forecast.html, 02.06.2025

\subsection{time horizon}

explain how there could be different time horizons etc. and what goes into the decision.
may be moved to Methods chapter?

\subsection{Different approaches to prediction models}
\subsubsection{Explanatory model}
\subsubsection{Time series models}
von https://otexts.com/fpp3/data-methods.html, bin nicht sicher, wieweit das wirklich
verwendete begriffe sind? bzw. wie relevant die sind, außer time series

\subsection{Data exploration}
\subsubsection{Decomposition}
for studying trends and seasonal patterns 

\subsection{Neural Networks}
General Info/Logic of Neural Networks / RNN /CNN (je nachdem)
\subsection{Statistik}

\subsubsection{SARIMA}

\subsubsection{LSTM}

\subsubsection{Prophet}



\section{Literature}


% \shortlorem

% \input{./sections/beispiele1.tex}

\section{Vorgehensweise}

\loremipsum
